Why Donors Donate?

### 2020-09-10 analysis/05_market_simulator.Rmd
Fixing Inputs

                        "Online (excluding social media)",
                        "Social Media",

@@

                        "Email",

@@

                        "Somewhat Liberal",
                        "Slightly Liberal",

@@

                        "Slightly Conservative",
                        "Somewhat Conservative",
                        "Extremely Conservative",

@@

                        "Somewhat Disagree",

@@

                        "Somewhat Agree",

@@

                        "Strongly Agree",

@@

                        "Very Unimportant",
                        "Somewhat Unimportant",

@@

                        "Somewhat Important",
                        "Very Important",

@@

                        "Atleast once a month",

@@

                        "Inactive Member",
                        "Active Member",

@@

                        "Never Married",

@@

                        "Highschool Graduate", 
                        "Some College",
                        "2 Year College",
                        "4 Year College",
                        "Graduate or Professional Degree",

@@

                        "More than Median - $61,372", 

@@

                        "Black", 
                        "American Indian", 

@@

                        "Pacific Islander", 

@@

                        "More than Median (> 36)")

@@

# Need to Fix
selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c("Atleast once a day",
                     "Once a week",
                     "Rarely"
                     ))

# Need to Fix
selectInput("p1_international_news",
         label = "Follow international news:",
         choices = c('Always',
                     "Sometimes",
                     "Never"))

selectInput("p1_news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online (excluding social media)",
                     "Social Media",
                     "Radio",
                     "Email",
                     "News app"),
         multiple = TRUE)

# Need to Fix
selectInput("p1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c('Most of the time',
                     'Some of the time',
                     "Only now and then",
                     "Hardly at all"))

selectInput("p1_travel_developing",
         label = "Travel to developing country:",
         choices = c('Does Travel', "Doesn't Travel"))

# Need to Fix
selectInput("p1_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("0", '1', '2', '3','4','5','6','7'))

>>>>

                        "Online (not social media)",
                        "Social media",

@@

                        "Email newsletter",

@@

                        "Somewhat liberal",
                        "Slightly liberal",

@@

                        "Slightly conservative",
                        "Somewhat conservative",
                        "Extremely conservative",

@@

                        "Somewhat disagree",

@@

                        "Somewhat agree",

@@

                        "Strongly agree",

@@

                        "Very unimportant",
                        "Somewhat unimportant",

@@

                        "Somewhat important",
                        "Very important",

@@

@@

                        "Inactive member",
                        "Active member",

@@

                        "Never married",

@@

                        "Highschool graduate", 
                        "Some college",
                        "2 year college",
                        "4 year college",
                        "Graduate or orofessional degree",

@@

                        "More than median of $61,372", 

@@

                        "Black or African American", 
                        "American Indian or Alaska Native", 

@@

                        "Native Hawaiian or Pacific Islander", 

@@

                        "More than median age of 36")

@@

selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c("Rarely",
                     "Once a week",
                     "Atleast once a day"))

selectInput("p1_international_news",
         label = "Follow international news:",
         choices = c("Never",
                     "Sometimes",
                     'Always'))

selectInput("p1_news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online (not social media)",
                     "Social media",
                     "Radio",
                     "Email newsletter",
                     "News app"),
         multiple = TRUE)

# Need to Check on Hold out
selectInput("p1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not Often",
                     "Often"))

selectInput("p1_travel_developing",
         label = "Travel to developing country:",
         choices = c('No', "Yes"))

selectInput("p1_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("Extremely liberal",
                     "Somewhat liberal",
                     "Slightly liberal",
                     "Moderate",
                     "Slightly conservative",
                     "Somewhat conservative",
                     "Extremely conservative"))
